Biases in Planet Occurrence Caused by Unresolved Binaries in Transit Surveys

### 2018-04-17 paper/main.tex
add another KM comment
fix typo

We can now assess the severity of the errors, for a given value of the
binary-to-single ratio $n\b/n\s$. For stars with masses from 0.7 to
1.3~$M_\odot$, \citet{raghavan_survey_2010} found the multiplicity
fraction~--~the fraction of systems in a volume-limited sample that
are multiple~--~to be 0.44.  Assuming all multiple systems are
binaries, this gives a binary fraction
\begin{equation}
  \frac{n\b}{n\s + n\b} \approx 0.44,
\end{equation}
which implies $n\b/n\s \approx 0.79$.  Of course not all of these
binaries are ``twin'' binaries as we have assumed in our simple
calculation.  Later, in Section~\ref{sec:general_formula}, we will
allow for a continuum of properties for the secondary stars. For now,
we might guess that only a tenth of the binaries have pairs of stars
close enough in brightness to produce errors as significant as those
we have been considering.  Adopting the value $n\b/n\s\approx0.05$, we
find
\begin{equation}
    \frac{\Lambda_{{\rm{a}},r}}{\Lambda_r} = 0.88,~~
    \frac{\Lambda_{{\rm{a}},r/\sqrt{2}}}{\Lambda_r} = 0.25.
    \label{eq:ratios}
\end{equation}
All together, the various effects produce biases of order 10\% in the
occurrence rates.  We will see that this level of error is
characteristic of many of our more complicated models as well.

@@

\added{
It seems likely that to consistently account for binarity in
planet occurrence rate calculation, one must stipulate a
population inference model with parameters controlling both the
planet and binary star populations.
Given the difficulty of writing a correct likelihood function
for such a model, one feasible computational approach might be to
forward-model transit surveys with likelihood-free 
techniques~\citep[\textit{e.g.},][]{morehead_understanding_2016,hsu_improving_2018}.
The NASA {\it TESS} mission should provide ample opportunity
for such a study.
}

>>>>

We can now assess the severity of the errors, for a given value of the
binary-to-single ratio $n\b/n\s$. For stars with masses from 0.7 to
1.3~$M_\odot$, \citet{raghavan_survey_2010} found the multiplicity
fraction~--~the fraction of systems in a volume-limited sample that
are multiple~--~to be 0.44.  Assuming all multiple systems are
binaries, this gives a binary fraction
\begin{equation}
  \frac{n\b}{n\s + n\b} \approx 0.44,
\end{equation}
which implies $n\b/n\s \approx 0.79$.  Of course not all of these
binaries are ``twin'' binaries as we have assumed in our simple
calculation.  Later, in Section~\ref{sec:general_formula}, we will
allow for a continuum of properties for the secondary stars. For now,
we might guess that only a tenth of the binaries have pairs of stars
close enough in brightness to produce errors as significant as those
we have been considering.  Adopting the value $n\b/n\s\approx0.05$, we
find
\begin{equation}
    \frac{\Lambda_{{\rm{a}},r}}{\Lambda_r} = 0.88,~~
    \frac{\Lambda_{{\rm{a}},r/\sqrt{2}}}{\Lambda_r} = 0.25.
    \label{eq:ratios}
\end{equation}
\added{The apparent and true rates are illustrated in 
Figure~\ref{fig:occ_rate_model_1}.}
All together, the various effects produce biases of order 10\% in the
occurrence rates.  We will see that this level of error is
characteristic of many of our more complicated models as well.

@@

\added{
It seems likely that to consistently account for binarity, one
must use a population inference model with parameters
controlling both the planet and binary star populations.
Given the difficulty of writing a correct likelihood function
for such a model, one feasible computational approach might be to
forward-model transit surveys with likelihood-free 
techniques~\citep[\textit{e.g.},][]{morehead_understanding_2016,hsu_improving_2018}.
The NASA {\it TESS} mission will likely open up this avenue of research,
since its target stars are close and bright.
}
